Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-09-23 ms.tex
editing phrasing of paragraph discussing Fig. 8

Integrating $dE/dt d\nu$ from Eq. \ref{eq:dEdtdnu} over all times should give a distribution for the emitted frequencies. It is expected that this time-integrated spectrum of the response to an impulse will agree well with the solution for the $H_0$ steady-state spectrum (Eq. \ref{eq:H0surf}). Dividing by the energy $E$, we find the probability distribution
\be \label{eq:spectrum}
P(\nu) & = &  \frac{16\pi^2 R}{3k\phi E}  \sum_{nm} (-1)^n \gamma_{nm}^{-1} J_{nm}(\sigma).
\ee
Integrating over $\nu$ gives unity according to the sum rule in Eq. \ref{eq:sumrule}. In Fig. \ref{fig:steadystate}, the resulting spectrum is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady-state $J=0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Eq. \ref{eq:H0surf_sum}. This graphic illustrates the physics modeled by each variable in the expansion. For example, the spatial modes contribute to the solutions' accuracy in the core of the line. If more spatial modes were calculated, the agreement between the lines extends further into the core. If additional frequency modes are calculated, faster-oscillating terms are incorporated into the sum over the imaginary frequency variable $\gamma$ which create more perfect cancellations with the lower-order terms, reducing the ``ringing'' seen in the time-integrated spectrum. Extending the calculation deep into the line core by adding additional spatial modes could have an impact on the accuracy of the escape time distribution, but this would only affect the distribution at late times since core photons are trapped for a longer duration before escaping. This was the motivation for choosing a comparatively low number of spatial eigenmodes with respect to the number of frequency eigenmodes calculated. As a result of this choice, we expect that our semianalytic approach will underestimate the number of escaping photon at late times as compared with the Monte Carlo.

>>>>

Integrating $dE/dt d\nu$ from Eq. \ref{eq:dEdtdnu} over all times should give a distribution for the emitted frequencies. It is expected that this time-integrated spectrum of the response to an impulse will agree well with the solution for the $H_0$ steady-state spectrum (Eq. \ref{eq:H0surf}). Dividing by the energy $E$, we find the probability distribution
\be \label{eq:spectrum}
P(\nu) & = &  \frac{16\pi^2 R}{3k\phi E}  \sum_{nm} (-1)^n \gamma_{nm}^{-1} J_{nm}(\sigma).
\ee
Integrating over $\nu$ gives unity according to the sum rule in Eq. \ref{eq:sumrule}.

In Fig. \ref{fig:steadystate}, the resulting spectrum is shown for a sum up to $n=20$ and $m=500$ (labelled ``Time-integrated'') as compared with two analytic solutions: the steady state $H_0$ solution with no time dependence (``Steady State'') and the result for summing \textit{only} spatial modes in the eigenfunction expansion with the time dependence ignored (``Partial Sum''), as in Eq. \ref{eq:H0surf_sum}. Additional spatial modes contribute to the solutions' accuracy in the core of the line. If more spatial modes are calculated, the agreement with the steady state spectrum extends further toward the line core, with an infinite number of modes required for convergence at $x_s$. If additional frequency modes are calculated, faster-oscillating terms are incorporated into the sum over $\gamma$ which create more perfect cancellations with the lower-order terms, reducing the ``ringing'' seen in the time-integrated spectrum. Extending the calculation deep into the line core by adding additional spatial modes could have an impact on the accuracy of the escape time distribution, but this would only affect the distribution at late times since photons are trapped for a longer duration before escaping. This was the motivation for choosing a comparatively low number of spatial eigenmodes with respect to the number of frequency eigenmodes calculated. %TODO: Include? As a result of this choice, we expect that our semianalytic approach will underestimate the number of escaping photon at late times as compared with the Monte Carlo.
